---
title: "Script Run-Times Based Logfiles"
author: "Peter von Rohr"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Script Run-Times Based Logfiles}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r examplelog, echo=FALSE}
s_log_path <- system.file("extdata/timing-log/prepPhaeprep.log", package = 'zwsroutinetools')
con_log <- file(description = s_log_path)
vec_log <- readLines(con = con_log)
close(con = con_log)
```

Based on our effort to standardize the scripts running during a GE-analysis, every script should print a start message and an end message. The minimal version of a start message or an end message is just the date and time. An example of such start and end messages is shown below. 

```{r showfirstline, echo=FALSE}
cat(vec_log[1], "\n")
cat(vec_log[length(vec_log)], "\n")
```

## Compute Runtimes
The difference between the two times shown in the start and end messages can be used to get a basic estimate of the runtime of a script. 

